Distortion-corrected kernel density estimate on Riemannian manifolds

### 2022-10-10 paper/paper.tex
Add appendix plots for other ML methods

\caption{\label{tab:fourdhdrtable}Percentage comparison of correct highest density regions in density estimation of four manifold learning embeddings.}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{l|>{}c>{}c|>{}c>{}c|>{}c>{}c|>{}cc}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{2}{c}{ISOMAP} & \multicolumn{2}{c}{LLE} & \multicolumn{2}{c}{Laplacian Eigenmaps} & \multicolumn{2}{c}{UMAP} \\
\cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5} \cmidrule(l{3pt}r{3pt}){6-7} \cmidrule(l{3pt}r{3pt}){8-9}
  & DC-KDE & KDE & DC-KDE & KDE & DC-KDE & KDE & DC-KDE & KDE\\
\midrule
>99 & \cellcolor[HTML]{E6E6E6}{\textbf{0.830}} & 0.490 & \cellcolor[HTML]{E6E6E6}{\textbf{0.830}} & 0.240 & \cellcolor[HTML]{E6E6E6}{\textbf{0.840}} & 0.840 & \cellcolor[HTML]{E6E6E6}{\textbf{0.770}} & 0.000\\
99 & \cellcolor[HTML]{E6E6E6}{\textbf{0.818}} & 0.685 & \cellcolor[HTML]{E6E6E6}{\textbf{0.805}} & 0.478 & \cellcolor[HTML]{E6E6E6}{\textbf{0.815}} & 0.595 & \cellcolor[HTML]{E6E6E6}{\textbf{0.632}} & 0.032\\
90 & \cellcolor[HTML]{E6E6E6}{0.919} & \textbf{0.926} & \cellcolor[HTML]{E6E6E6}{\textbf{0.921}} & 0.900 & \cellcolor[HTML]{E6E6E6}{\textbf{0.798}} & 0.440 & \cellcolor[HTML]{E6E6E6}{\textbf{0.779}} & 0.428\\
50 & \cellcolor[HTML]{E6E6E6}{0.825} & \textbf{0.851} & \cellcolor[HTML]{E6E6E6}{0.831} & \textbf{0.848} & \cellcolor[HTML]{E6E6E6}{\textbf{0.659}} & 0.512 & \cellcolor[HTML]{E6E6E6}{\textbf{0.623}} & 0.448\\
5 & \cellcolor[HTML]{E6E6E6}{0.508} & \textbf{0.556} & \cellcolor[HTML]{E6E6E6}{0.514} & \textbf{0.562} & \cellcolor[HTML]{E6E6E6}{\textbf{0.431}} & 0.000 & \cellcolor[HTML]{E6E6E6}{\textbf{0.220}} & 0.000\\
% \addlinespace
1 & \cellcolor[HTML]{E6E6E6}{0.080} & \textbf{0.190} & \cellcolor[HTML]{E6E6E6}{0.090} & \textbf{0.230} & \cellcolor[HTML]{E6E6E6}{\textbf{0.000}} & 0.000 & \cellcolor[HTML]{E6E6E6}{\textbf{0.000}} & 0.000\\
\bottomrule
\end{tabular}}
\end{table}

@@

>>>>

\caption{\label{tab:fourdhdrtable}Percentage comparison of correct highest density regions in density estimation of four manifold learning embeddings.}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{l|>{}c>{}c|>{}c>{}c|>{}c>{}c|>{}cc}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{2}{c}{ISOMAP} & \multicolumn{2}{c}{LLE} & \multicolumn{2}{c}{Laplacian Eigenmaps} & \multicolumn{2}{c}{UMAP} \\
\cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5} \cmidrule(l{3pt}r{3pt}){6-7} \cmidrule(l{3pt}r{3pt}){8-9}
  & DC-KDE & KDE & DC-KDE & KDE & DC-KDE & KDE & DC-KDE & KDE\\
\midrule
>99 & \cellcolor[HTML]{E6E6E6}{\textbf{0.830}} & 0.490 & \cellcolor[HTML]{E6E6E6}{\textbf{0.830}} & 0.240 & \cellcolor[HTML]{E6E6E6}{\textbf{0.840}} & 0.840 & \cellcolor[HTML]{E6E6E6}{\textbf{0.770}} & 0.000\\
99 & \cellcolor[HTML]{E6E6E6}{\textbf{0.818}} & 0.685 & \cellcolor[HTML]{E6E6E6}{\textbf{0.805}} & 0.478 & \cellcolor[HTML]{E6E6E6}{\textbf{0.815}} & 0.595 & \cellcolor[HTML]{E6E6E6}{\textbf{0.632}} & 0.032\\
90 & \cellcolor[HTML]{E6E6E6}{0.919} & \textbf{0.926} & \cellcolor[HTML]{E6E6E6}{\textbf{0.921}} & 0.900 & \cellcolor[HTML]{E6E6E6}{\textbf{0.798}} & 0.440 & \cellcolor[HTML]{E6E6E6}{\textbf{0.779}} & 0.428\\
50 & \cellcolor[HTML]{E6E6E6}{0.825} & \textbf{0.851} & \cellcolor[HTML]{E6E6E6}{0.831} & \textbf{0.848} & \cellcolor[HTML]{E6E6E6}{\textbf{0.659}} & 0.512 & \cellcolor[HTML]{E6E6E6}{\textbf{0.623}} & 0.448\\
5 & \cellcolor[HTML]{E6E6E6}{0.508} & \textbf{0.556} & \cellcolor[HTML]{E6E6E6}{0.514} & \textbf{0.562} & \cellcolor[HTML]{E6E6E6}{\textbf{0.431}} & 0.000 & \cellcolor[HTML]{E6E6E6}{\textbf{0.220}} & 0.000\\
\addlinespace
1 & \cellcolor[HTML]{E6E6E6}{0.080} & \textbf{0.190} & \cellcolor[HTML]{E6E6E6}{0.090} & \textbf{0.230} & \cellcolor[HTML]{E6E6E6}{\textbf{0.000}} & 0.000 & \cellcolor[HTML]{E6E6E6}{\textbf{0.000}} & 0.000\\
\bottomrule
\end{tabular}}
\end{table}

@@

\hypertarget{twinpeaksappe}{%
\section{Appendix: Rank comparison plots for twin peaks mapping}\label{twinpeaksappe}}

This appendix contains the comparison plots for the density rank between DC-KDE and KDE using different manifold learning algorithms, similar to \autoref{fig:tpisomapden}, \autoref{fig:tptsneden}, and \autoref{fig:tpisomapvs4ml}. By comparing these plots, it could be concluded that DC-KDE could categorize the density ranks into highest density regions more accurately than KDE. By correcting the distortion in different manifold learning embeddings, DC-KDE is more robust in identifying the lowest density regions, which are usually used to detect anomalies.

{\centering \includegraphics[width=1\linewidth]{figures/Twin Peak2000_densityrank_comparison_lle_radius8_r0_5_logrank_rec_colprob_smallblocks3_crossfalse}

\caption{Scatterplot of true density and estimated density ranks of LLE embedding for DC-KDE and KDE, with colors indicating the absolute rank errors weighted by the sum of true and estimated ranks. DC-KDE shows a strong linear positive relationship with a higher rank correlation compared to KDE.}\label{fig:tplleden}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{figures/Twin Peak2000_densityrank_comparison_le_radius8_r0_5_logrank_rec_colprob_smallblocks3_crossfalse}

\caption{Scatterplot of true density and estimated density ranks of Laplaxian Eigenmaps embedding for DC-KDE and KDE, with colors indicating the absolute rank errors weighted by the sum of true and estimated ranks. DC-KDE shows a strong linear positive relationship with a higher rank correlation compared to KDE.}\label{fig:tpleden}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{figures/Twin Peak2000_densityrank_comparison_umap_radius8_r0_5_logrank_rec_colprob_smallblocks3_crossfalse}

\caption{Scatterplot of true density and estimated density ranks of UMAP embedding for DC-KDE and KDE, with colors indicating the absolute rank errors weighted by the sum of true and estimated ranks. DC-KDE shows a strong linear positive relationship with a higher rank correlation compared to KDE.}\label{fig:tpumapden}
\end{figure}

{\centering \includegraphics[width=0.95\linewidth]{figures/Twin Peak2000_density_compare_llevs4ml_radius8_r0_5_rank}

\caption{Comparison of outliers found by one manifold learning method compared to the other four for DC-KDE (on the left panel) and KDE (on the right panel). The four colors and shapes represents the four gaussian kernels in the 2-D meta data. Outliers found by DC-KDE are more consistent regardless of the manifold learning embedding.}\label{fig:tpllevs4ml-1}
\end{figure}
\begin{figure}

{\centering \includegraphics[width=0.95\linewidth]{figures/Twin Peak2000_density_compare_levs4ml_radius8_r0_5_rank}

\caption{Comparison of outliers found by one manifold learning method compared to the other four for DC-KDE (on the left panel) and KDE (on the right panel). The four colors and shapes represents the four gaussian kernels in the 2-D meta data. Outliers found by DC-KDE are more consistent regardless of the manifold learning embedding.}\label{fig:tpllevs4ml-2}
\end{figure}
\begin{figure}

{\centering \includegraphics[width=0.95\linewidth]{figures/Twin Peak2000_density_compare_tsnevs4ml_radius8_r0_5_rank}

\caption{Comparison of outliers found by one manifold learning method compared to the other four for DC-KDE (on the left panel) and KDE (on the right panel). The four colors and shapes represents the four gaussian kernels in the 2-D meta data. Outliers found by DC-KDE are more consistent regardless of the manifold learning embedding.}\label{fig:tpllevs4ml-3}
\end{figure}
\begin{figure}

{\centering \includegraphics[width=0.95\linewidth]{figures/Twin Peak2000_density_compare_umapvs4ml_radius8_r0_5_rank}

\caption{Comparison of outliers found by one manifold learning method compared to the other four for DC-KDE (on the left panel) and KDE (on the right panel). The four colors and shapes represents the four gaussian kernels in the 2-D meta data. Outliers found by DC-KDE are more consistent regardless of the manifold learning embedding.}\label{fig:tpllevs4ml-4}
\end{figure}
